Comparison of V4 region and long 16S seqs for Asaia OTU from fruit fly larvae
========================================================

```{r load packages and data, echo=FALSE}
library("phyloseq")
library("ggplot2")
#import data to phyloseq
setwd("~/Documents/UTS/skin_microbiome/16S_project/DPI/seq_data/run2_nectar/Asaia_betadiv")
#Define file paths
map<-import_qiime_sample_data("mapping3.txt")
biom_otu_table<- import_biom("otu_table_mc1_w_tax_no_pynast_failures_json.biom","rep_set.tre")
biom_otu_table_v4<-import_biom("otu_table_asaia_v4_no_pynast_failures_json.biom","rep_set_v4.tre")
asaia_data_long <- merge_phyloseq(biom_otu_table,map)
colnames(tax_table(asaia_data_long)) = c("Domain", "Phylum", "Class", "Order", 
                                    "Family", "Genus", "Species")
asaia_data_v4 <- merge_phyloseq(biom_otu_table_v4,map)
colnames(tax_table(asaia_data_v4)) = c("Domain", "Phylum", "Class", "Order", 
                                         "Family", "Genus", "Species")
```
The V4 region was extracted from the long sequences, and two phyloseq objects created with either the long 16S sequences, or extracted V4 region sequences.
```{r show characteristics of phyloseq objects}
asaia_data_long
asaia_data_v4
sample_sums(asaia_data_long)
sample_sums(asaia_data_v4)
```
Analysis of long seqs rarefied to 100 seqs per sample
```{r rarefaction and unifrac calculations, echo=FALSE}
asaia_rare100_long<-rarefy_even_depth(asaia_data_long, rngseed=511, replace=FALSE, sample.size=100)
asaia_wu_ord<-ordinate(asaia_rare100_long, method="PCoA", distance="wunifrac")
asaia_uu_ord<-ordinate(asaia_rare100_long, method="PCoA", distance="unifrac")
```
```{r fig.width=8, fig.height=6, echo=FALSE}
plot_richness(asaia_rare100_long, measures="Observed", x="location", title="observed richness long 16S, 100 seqs per sample")
plot_ordination(asaia_rare100_long, asaia_wu_ord, color="Source", title="PCoA of weighted unifrac all\nlong 16S, 100 seqs per sample")+
  scale_color_brewer(palette="Paired")
plot_ordination(asaia_rare100_long, asaia_uu_ord, color="Source", title="PCoA of unweighted unifrac all\nlong 16S, 100 seqs per sample")+
  scale_color_brewer(palette="Paired")
```

Remove Buxton Peach A for better visualisation of other samples

```{r fig.width=8, fig.height=6, echo=FALSE}
asaia_rare_sub<-subset_samples(asaia_rare100_long, Source!="Buxton_Peach_A")
sample_names(asaia_rare_sub)
asaia_sub_wu_ord<-ordinate(asaia_rare_sub, method="PCoA", distance="wunifrac")
plot_ordination(asaia_rare_sub, asaia_sub_wu_ord, color="Source", title="PCoA of weighted unifrac without Buxton Peach A\nlong 16S, 100 seqs per sample")+scale_color_brewer(palette="Paired")
asaia_sub_uu_ord<-ordinate(asaia_rare_sub, method="PCoA", distance="unifrac")
plot_ordination(asaia_rare_sub, asaia_sub_uu_ord, color="Source", title="PCoA of unweighted unifrac without Buxton Peach A\nlong 16S, 100 seqs per sample")+
  scale_color_brewer(palette="Paired")
```
Further remove Buxton Peach E for better visualisation of other samples
```{r fig.width=8, fig.height=6, echo=FALSE}
asaia_rare_sub2<-subset_samples(asaia_rare_sub, !(Source%in%c("Buxton_Peach_A","Buxton_Peach_E")))
sample_names(asaia_rare_sub2)
asaia_sub2_wu_ord<-ordinate(asaia_rare_sub2, method="PCoA", distance="wunifrac")
plot_ordination(asaia_rare_sub2, asaia_sub2_wu_ord, color="Source", title="PCoA of weighted unifrac without Buxton Peach A or E\nlong 16S, 100 seqs per sample")+
  scale_color_brewer(palette="Paired")
```
Repeat with V4 region extracted from seqs
```{r fig.width=8, fig.height=6, echo=FALSE}
asaia_rare100_v4<-rarefy_even_depth(asaia_data_v4, rngseed=511, replace=FALSE, sample.size=100)
plot_richness(asaia_rare100_v4, measures="Observed", x="location", title="Observed unique sequences of Asaia sp.\nV4 region 100 seqs")
asaia_v4_wu_ord<-ordinate(asaia_rare100_v4, method="PCoA", distance="wunifrac")
asaia_v4_uu_ord<-ordinate(asaia_rare100_v4, method="PCoA", distance="unifrac")
plot_ordination(asaia_rare100_v4, asaia_v4_wu_ord, color="Source", title="PCoA of weighted unifrac all\nV4 region 100 seqs")+
  scale_color_brewer(palette="Paired")
plot_ordination(asaia_rare100_v4, asaia_v4_uu_ord, color="Source", title="PCoA of unweighted unifrac all\nV4 region 100 seqs")+
  scale_color_brewer(palette="Paired")
asaia_v4_rare_sub<-subset_samples(asaia_rare100_v4, Source!="Buxton_Peach_A")
sample_names(asaia_v4_rare_sub)
asaia_v4_sub_wu_ord<-ordinate(asaia_v4_rare_sub, method="PCoA", distance="wunifrac")
plot_ordination(asaia_v4_rare_sub, asaia_v4_sub_wu_ord, color="Source", title="PCoA of weighted unifrac without Buxton Peach A\nV4 region 100 seqs")+
  scale_color_brewer(palette="Paired")
asaia_v4_sub_uu_ord<-ordinate(asaia_v4_rare_sub, method="PCoA", distance="unifrac")
plot_ordination(asaia_v4_rare_sub, asaia_v4_sub_uu_ord, color="Source", title="PCoA of unweighted unifrac without Buxton Peach A\nV4 region 100 seqs")+
  scale_color_brewer(palette="Paired")
asaia_v4_rare_sub2<-subset_samples(asaia_v4_rare_sub, !(Source%in%c("Buxton_Peach_A","Buxton_Peach_E")))
sample_names(asaia_v4_rare_sub2)
asaia_v4_sub2_wu_ord<-ordinate(asaia_v4_rare_sub2, method="PCoA", distance="wunifrac")
plot_ordination(asaia_v4_rare_sub2, asaia_v4_sub2_wu_ord, color="Source", title="PCoA of weighted unifrac without Buxton Peach A or E\nV4 region 100 seqs")+
  scale_color_brewer(palette="Paired")
```

